The problem and promise of scale in multilayer networks

### 2020-01-23 paper/glossary.rmd
add terms to gloss
Update glossary.rmd

@@

>>>>

**Connective redundancy**: 1 - (neighborhood / degree) When connective redundancy is 0, all edges on all layers are necessary to preserve the social ties.[QW: FROM ALEC'S WRITING IN THE MS]

**Degree centrality**:

**Degree deviation**:

@@

**Multidegree**:

**Neighbours**: degree within a network layer.[QW: FROM ALEC'S WRITING IN THE MS]

**Relevance**: neighborhood of specific layer  / neighbourhood of full ml net. This is the proportion of neighbors present on the layer of focus. Comparing across, it tells you which layers are most important for each individual. [QW: FROM ALEC'S WRITING IN THE MS]
